A spatio-temporal analysis of the environmental correlates of COVID-19 incidence in Spain

### 2020-05-12 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.Rmd
Added missing reference to aemet

The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `aemet` [], `ggthemes` [@Arnold2019], `gridExtra` [@Auguie2017gridextra], `kableExtra` [@Zhu2019], `knitr` [@Xie2014; @Xie2015], `lubridate` [@Grolemund2011dates], `plm` [@Millo2017robust], `rticles` [@Allaire2020], `sf` [@Pebesma2018], `spdep` [@Bivand2013], spsur [@Angulo2020spsur] `tidyverse` [@Wickham2019], `units` [@Pebesma2016].

>>>>

The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `aemet` [@Rodriguez2018aemet], `ggthemes` [@Arnold2019], `gridExtra` [@Auguie2017gridextra], `kableExtra` [@Zhu2019], `knitr` [@Xie2014; @Xie2015], `lubridate` [@Grolemund2011dates], `plm` [@Millo2017robust], `rticles` [@Allaire2020], `sf` [@Pebesma2018], `spdep` [@Bivand2013], spsur [@Angulo2020spsur] `tidyverse` [@Wickham2019], `units` [@Pebesma2016].

### 2020-05-12 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.tex
Added missing reference to aemet

The following \texttt{R} packages were used in the course of this
investigation and the authors wish to acknowledge their developers:
\texttt{aemet} {[}{]}, \texttt{ggthemes} (Arnold, 2019),
\texttt{gridExtra} (Auguie, 2017), \texttt{kableExtra} (Zhu, 2019),
\texttt{knitr} (Xie, 2015, 2014), \texttt{lubridate} (Grolemund and
Wickham, 2011), \texttt{plm} (Millo, 2017), \texttt{rticles} (Allaire et
al., 2020), \texttt{sf} (Pebesma, 2018), \texttt{spdep} (Bivand et al.,
2013), spsur (Angulo et al., 2020) \texttt{tidyverse} (Wickham et al.,
2019), \texttt{units} (Pebesma et al., 2016).

@@

>>>>

The following \texttt{R} packages were used in the course of this
investigation and the authors wish to acknowledge their developers:
\texttt{aemet} (Rodriguez-Sanchez et al., 2018), \texttt{ggthemes}
(Arnold, 2019), \texttt{gridExtra} (Auguie, 2017), \texttt{kableExtra}
(Zhu, 2019), \texttt{knitr} (Xie, 2015, 2014), \texttt{lubridate}
(Grolemund and Wickham, 2011), \texttt{plm} (Millo, 2017),
\texttt{rticles} (Allaire et al., 2020), \texttt{sf} (Pebesma, 2018),
\texttt{spdep} (Bivand et al., 2013), spsur (Angulo et al., 2020)
\texttt{tidyverse} (Wickham et al., 2019), \texttt{units} (Pebesma et
al., 2016).

@@

\leavevmode\hypertarget{ref-Rodriguez2018aemet}{}%
Rodriguez-Sanchez, F., Balao, F., Gámez, D., 2018. Aemet: Obtain
climatic and meteorological data from spanish meteorological agency
(aemet).
